\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage[margin=1in]{geometry}
\usepackage{natbib}
\usepackage{caption}
\usepackage{enumitem}

\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}

\title{Bankai: Ultra-Sparse Adaptation of 1-Bit LLMs via XOR Patches}

\author{
  Nikshep Saravanan \\
  \texttt{github.com/nikshepsvn/bankai}
}

\date{April 2, 2026}

\begin{document}
\maketitle

% ============================================================
\begin{abstract}
True 1-bit large language models have no post-training adaptation method.
LoRA, fine-tuning, and quantization-aware training all require continuous
weights or gradients that binary models lack. We introduce \textbf{Bankai},
the first post-training adaptation method for true 1-bit LLMs, using
bitwise XOR operations on binary weights. Bankai patches are sparse XOR
bitmasks that modify model weights in-place with a single bitwise operation,
incur zero inference overhead, and compress to around one kilobyte.

We validate on Bonsai~8B (PrismML, 2026), a true 1-bit, 8.2~billion
parameter language model. Through eight experiments, we demonstrate that:
(1)~binary MLP weights exhibit massive redundancy;
(2)~scale-guided bit flips produce $3.88\times$ more behavioral impact
than random flips;
(3--4)~greedy search yields patches that correct specific calculus failures
in free generation;
(5)~patches trained on few probes memorize rather than generalize; and
(6)~training on diverse probe variations produces patches that
\textbf{generalize to held-out prompts}---fixing 4~of~17 problems
the base model gets wrong (23.5\%) with zero breakage on the 13 it
already solves.
\end{abstract}

% ============================================================
\section{Introduction}

The emergence of true 1-bit large language models---where every weight is
a single bit---represents a fundamental shift in model efficiency.
Bonsai~8B~\citep{prismml2026} stores 8.2~billion parameters in 1.15~GB,
runs at 44~tokens/second on an iPhone, and achieves benchmark scores
competitive with full-precision 8B~models.

However, these models present a novel challenge: \textbf{they cannot be
adapted after deployment}. Every existing method for post-training
adaptation requires continuous-valued operations:

\begin{itemize}[nosep]
  \item \textbf{LoRA}~\citep{hu2021lora} adds low-rank weight deltas in
    float space.
  \item \textbf{Fine-tuning} backpropagates continuous gradients through
    differentiable weights.
  \item \textbf{Quantization-aware training} adjusts weights during
    pre-training, not after deployment.
\end{itemize}

None of these apply to a model whose weights are single bits. Once a 1-bit
model is deployed, it is frozen.

We introduce \textbf{Bankai}, the first post-training adaptation method
for true 1-bit LLMs. The key insight: because weights are bits, the
``diff'' between two behavioral states is a bitwise XOR mask. Where the
mask has a~1, a weight flipped. Where it has a~0, nothing changed. For
nearby behavioral variants, this mask is sparse---enabling patches that
modify $0.007\%$ of weights (${\sim}1$~KB) with zero inference overhead,
microsecond application, and exact reversibility.

We validate Bankai on Bonsai~8B through six experiments, progressing from
mechanism validation (Experiments~1--2), through targeted correction
(Experiments~3--4), to generalization testing (Experiments~5--6). We find
that patches trained on 6~probes memorize specific prompts, but patches
trained on 60~diverse probes generalize to held-out problems---fixing
4~of~17 incorrect answers with zero collateral damage.

\subsection{Contributions}

\begin{enumerate}[nosep]
  \item \textbf{The first post-training adaptation method for true 1-bit
    LLMs.} Existing methods (LoRA, fine-tuning, QAT) require continuous
    weights or gradients and are inapplicable to binary architectures.
  \item \textbf{Scale-guided targeting.} Per-group FP16 scale factors
    predict which weight regions are most behaviorally sensitive, enabling
    $3.88\times$ more efficient search than uniform random sampling.
  \item \textbf{Layer-level functional specialization in 1-bit
    architectures.} Early layers (1--4) and the penultimate layer~(34)
    are load-bearing, while middle layers (17--21) contribute minimally.
  \item \textbf{A characterization of generalization.} Patches trained on
    few probes memorize; diverse training produces generalization. This
    is the first empirical characterization of how XOR patches learn.
  \item \textbf{An open toolkit and patch format} for reproducible
    creation, application, and evaluation of XOR patches.
\end{enumerate}

% ============================================================
\section{Background}

\subsection{True 1-Bit vs.\ Ternary Models}

The distinction between true 1-bit and ternary models is critical.
BitNet~b1.58~\citep{wang2023bitnet,ma2025bitnet} uses ternary weights
$\{-1, 0, +1\}$, requiring 2~bits per weight in storage. Despite the
``1-bit'' branding, XOR on 2-bit ternary encodings produces invalid
states: $\text{XOR}(01, 10) = 11$, which has no valid ternary mapping.

Bonsai~8B~\citep{prismml2026} is a true 1-bit model where each weight
is a single bit: $0 \to -\text{scale}$, $1 \to +\text{scale}$. Weights
are packed as \texttt{uint32} arrays with per-group FP16 scale factors
(group size~128). This makes bitwise XOR a semantically valid operation.
As of April~2026, Bonsai~8B is the only production-quality true 1-bit LLM.

\subsection{Deployment Implications}

The properties of XOR patches---kilobyte-scale size, microsecond
application, zero inference overhead, instant reversibility---enable
a deployment model impossible with existing adaptation methods.
A library of domain patches (math, code, medical, legal), each
${\sim}1$~KB, can be hot-swapped at inference time on a phone.
The base model stays at 1.15~GB; a thousand patches add 1~MB.
LoRA adapters are ${\sim}100$~MB each, add per-token latency,
and require weight reloading to swap.

% ============================================================
\section{Related Work}

\textbf{Low-rank adaptation.}
LoRA~\citep{hu2021lora} and its variants (QLoRA~\citep{dettmers2023qlora};
DoRA) reduce fine-tuning cost via low-rank weight deltas. These require
continuous weights and are not applicable to true 1-bit architectures.

\textbf{Compact adaptation.}
RECAST~\citep{xu2024recast} reduces task-specific parameters to fewer
than~50 via weight reconstruction on continuous-weight models.

\textbf{Binary neural networks.}
XOR-Net~\citep{bulat2020xornet} and XNOR-Net~\citep{rastegari2016xnor}
use binary operations for efficient forward passes, not post-training
behavioral modification.

\textbf{1-bit and sub-1-bit LLMs.}
BitNet~\citep{wang2023bitnet} introduced 1.58-bit LLM training.
STBLLM~\citep{dong2024stbllm} pushed compression below 1-bit and
observed that some weights in binarized LLMs can be randomly flipped
without significant performance degradation---a finding our
Experiment~1 independently confirms.

\textbf{Bit-flip attacks.}
\citet{rakin2019bitflip} showed that ${\sim}20$ targeted bit flips can
catastrophically degrade a quantized DNN. Subsequent work
(T-BFA~\citep{bai2021tbfa}; Versatile Weight Attack) refined targeted
attacks. This literature establishes that small numbers of bit flips
produce outsized behavioral effects---but focuses exclusively on
adversarial degradation. \textbf{Bankai inverts this mechanism:}
constructive bit flips for targeted capability improvement.

\textbf{Model editing.}
ROME~\citep{meng2022rome} and MEMIT~\citep{meng2023memit} perform
targeted factual edits on continuous-weight models. Bankai shares
the goal of minimal intervention but operates on binary weights for
behavioral (not factual) modification.

% ============================================================
\section{Methodology}

All experiments use Bonsai~8B (\texttt{prism-ml/Bonsai-8B-mlx-1bit}),
a true 1-bit, 8.2B~parameter model based on the Qwen3 architecture
(36~layers, 4096 hidden dim, GQA with 32/8~heads). Weights are packed
as \texttt{uint32} arrays with 1-bit group quantization
(\texttt{group\_size=128}). Experiments were run on Apple~M3 (24~GB).

\subsection{Logit Gap Probes}

We measure behavioral change via \textbf{logit gap probes}: pairs of
(correct\_token, wrong\_token) following a deterministic prompt. The
logit gap $G = \text{logit}(\text{correct}) - \text{logit}(\text{wrong})$
is a single-forward-pass measurement: positive means the model prefers
the correct answer. We use this as a fast proxy for behavioral change,
noting that logit improvement does not always translate to generation
improvement (see Section~\ref{sec:limitations}).

\subsection{Experiment~1: Random Bit Flip Robustness}

We flip $N$ random bits across all MLP weight tensors (5.4B~bits total)
and measure perplexity on a fixed 5-sentence eval set, for
$N \in \{100, 1\text{K}, 10\text{K}, 50\text{K}, 100\text{K}, 500\text{K}\}$
under four strategies: random across all layers, random in layers~16--24,
scale-guided medium (25th--75th percentile), and scale-guided high
(top~25\%).

\subsection{Experiment~2: Structured Flips and Layer Specialization}

For each of 36~layers, we flip all bits in the entire MLP and measure
logit gaps on 8~probes spanning arithmetic, code, geography, and
science. We then test row-level flips at varying counts (1--1024~rows)
in the most impactful layer and compare high-scale rows vs.\ random
rows at 64~rows.

\subsection{Experiment~3: Greedy Patch Search (Arithmetic)}

Greedy hill climbing over row-level flips in layers $[1, 2, 3, 4, 34]$
(selected from Experiment~2). Each iteration: sample a row weighted by
scale magnitude, flip all 4,096~bits, measure fitness, keep if improved,
revert if not. 200~iterations with 6~target probes (arithmetic) and
4~control probes (knowledge).

\textbf{Fitness function:}
\begin{equation}
  f = \frac{1}{|T|}\sum_{t \in T} (g_t - g_t^0)
    - \lambda \cdot \frac{1}{|C|}\sum_{c \in C} \max(0, g_c^0 - g_c)
\end{equation}
where $g_t, g_c$ are target and control logit gaps, superscript~$0$
denotes baselines, and $\lambda = 2.0$ penalizes control degradation.

\subsection{Experiment~4: Calculus Patch}

Same search targeting 6~calculus probes (polynomial differentiation,
second derivatives, integrals, primality, trigonometry, exponential
derivatives) where the base model fails deterministically (verified
across 5~runs). 300~iterations with screening optimization.

\subsection{Experiment~5: Variation Testing}

We generate 15~novel variations per probe category (90~total) and
measure sign flips (wrong$\to$right vs.\ right$\to$wrong) on the
Experiment~4 patch applied to these never-seen probes.

\subsection{Experiment~6: Generalization-Optimized Search}

Train on 60~probes (10~per category with diverse phrasings), hold out
30~probes (5~per category) for validation. Mean fitness, 300~iterations.
Search time scales roughly linearly with probe count:
6~probes $\to$ 13~min, 60~probes $\to$ 67~min.

\subsection{Experiment~7: Patch Stacking}

Apply the Experiment~3 math patch (72~flips) and Experiment~4 calculus
patch (70~flips) simultaneously via sequential XOR. Verify order
independence and reversibility. Test both math and calculus probes.

\subsection{Experiment~8: GSM8K Safety Check}

Run 50~GSM8K word problems with full generation (400~tokens) and answer
extraction. Compare accuracy with and without the Experiment~6
generalized patch to check for collateral damage on general math
reasoning.

% ============================================================
\section{Results}

\subsection{Experiment~1: Random Flips Are Absorbed}

\begin{table}[h]
\centering
\caption{Perplexity change under random bit flips in MLP weights.}
\begin{tabular}{@{}lll@{}}
\toprule
Flips & \% of MLP bits & Max Perplexity $\Delta$ \\
\midrule
100     & 0.000002\% & $< 0.01$ \\
10,000  & 0.0002\%   & $< 0.01$ \\
100,000 & 0.002\%    & $< 0.02$ \\
500,000 & 0.009\%    & $< 0.08$ \\
\bottomrule
\end{tabular}
\end{table}

The model is remarkably robust to random perturbation in MLP weights,
implying massive redundancy. (Attention weights, embeddings, and the
LM~head were not tested.)

\subsection{Experiment~2: Layer Impact and Scale-Guided Targeting}

\begin{table}[h]
\centering
\caption{Average absolute logit gap change ($|\Delta\text{gap}|$) when
  flipping the entire MLP of each layer range. 8~probes across 4~domains.}
\begin{tabular}{@{}lll@{}}
\toprule
Layer range & Avg $|\Delta\text{gap}|$ & Interpretation \\
\midrule
0--4 (early)        & 3.2--7.2 & High impact \\
5--16 (middle)      & 0.7--3.0 & Moderate, decreasing \\
17--21 (deep mid)   & 0.7--1.6 & \textbf{Lowest impact} \\
22--33 (late)       & 1.6--3.4 & Moderate, increasing \\
34 (penultimate)    & \textbf{9.0} & \textbf{Highest impact} \\
35 (final)          & 3.2 & High \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Scale-guided targeting:} At 64~rows in layer~34, high-scale
rows produce $3.88\times$ more behavioral impact than random rows
(avg $|\Delta\text{gap}|$: 0.459 vs.\ 0.118). Layer effects appear
domain-specific across our probe set---layer~34 shifts physics by
$+13.8$ while shifting code by $-15.9$.

\subsection{Experiment~3: Arithmetic Patch}

200~iterations, 72~accepted flips, 7.5~minutes on M3. The \texttt{2+2}
probe flips from incorrect (prefers~5) to correct (prefers~4) in both
logit gap and free generation. The \texttt{7$\times$8} probe improves
at the logit level (prefers~56 over~54) but free generation produces~64
($=8\times8$)---a different wrong answer, illustrating the gap between
probe-based and generation-based evaluation.

\textbf{Patch:} 72~flips, 294,912~bits modified (0.005\%), 864~bytes.
No degradation on 4~measured control probes.

\subsection{Experiment~4: Calculus Patch}

300~iterations, 70~accepted flips, ${\sim}13$~minutes on M3. Two
deterministic failures corrected in free generation:

\begin{itemize}[nosep]
  \item \texttt{d/dx [x\^{}4 + 3x\^{}2] = 0}
    $\to$ \texttt{4x\^{}3 + 6x} \checkmark
  \item \texttt{The second derivative of x\^{}4 is 12x\^{}3}
    $\to$ \texttt{12x\^{}2} \checkmark
\end{itemize}

\textbf{Prompt sensitivity finding:} The primality probe
(\texttt{Is 97 prime?}) is sensitive to a trailing space---the base
model's answer flips from ``No'' to ``Yes'' without any patch. This
illustrates the fragility of single-token probes and motivates
diverse training sets (Experiment~6).

\textbf{Patch:} 70~flips, 286,720~bits (0.005\%), 840~bytes.
No degradation on 5~measured control probes.

\subsection{Experiment~5: Variation Testing (Negative Result)}

The Experiment~4 patch was tested on 90~novel variations (15~per
category). Sign-flip analysis:

\begin{table}[h]
\centering
\caption{Experiment~4 patch applied to 90~never-seen probes.}
\begin{tabular}{@{}lr@{}}
\toprule
Metric & Count \\
\midrule
Fixed (wrong $\to$ right) & 2 \\
Broke (right $\to$ wrong) & 5 \\
Stayed right & 57 \\
Stayed wrong & 26 \\
\midrule
Net sign flips & $-3$ \\
Base accuracy & 62/90 (68.9\%) \\
Patched accuracy & 59/90 (65.6\%) \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Finding:} The 6-probe patch memorizes specific prompts rather
than shifting capabilities. All 5~broken probes had borderline baseline
gaps ($< 1.2$).

\subsection{Experiment~6: Generalization-Optimized Search}

Motivated by Experiment~5's memorization finding, we trained on
60~probes (10~per category with diverse phrasings) and validated on
30~held-out probes.

\begin{table}[h]
\centering
\caption{Sign-flip analysis on training and held-out validation sets.}
\begin{tabular}{@{}lrr@{}}
\toprule
Metric & Training (60) & Validation (30) \\
\midrule
Fixed (wrong $\to$ right) & 4 & \textbf{4} \\
Broke (right $\to$ wrong) & 0 & \textbf{0} \\
Stayed right & 44 & 13 \\
Stayed wrong & 12 & 13 \\
\midrule
Accuracy & 44/60 $\to$ 48/60 & 13/30 $\to$ \textbf{17/30} \\
\bottomrule
\end{tabular}
\end{table}

Validation fixes span 4~categories: polynomial derivatives, second
derivatives, integrals, and primality. Trig and exponential derivative
categories saw zero fixes---a calculus-specific layer impact analysis
identified layers~5, 6, and~10 as high-impact for calculus but not
included in the search set, which may explain the gap.

The base model gets 17~of~30 validation probes wrong; the patch fixes
4~of~those~17 (23.5\%) while breaking none of the 13 it already solves.

\textbf{Patch:} 93~flips, 380,928~bits (0.007\%), 1,116~bytes.
No degradation on 5~measured control probes.

\subsection{Experiment~7: Patch Stacking}

The Experiment~3 math patch (72~flips) and Experiment~4 calculus patch
(70~flips) have zero row overlap, yielding 142~combined flips.
Stacking is mechanically correct: order-independent (math+calc gives
identical results to calc+math) and perfectly reversible (zero drift
after removal).

However, behavioral composition shows interference. The math patch
damages \texttt{poly\_deriv} ($-1.59$) while the calculus patch improves
it ($+2.77$); stacked, they partially cancel ($+0.19$). Overall:
individual patches each fix~2 and break~1 probe; the stacked patch
fixes~1 and breaks~0.

\textbf{Finding:} Patches compose algebraically but interfere
behaviorally. Stacking is safer (fewer breakages) but less effective
(fewer fixes) than individual patches. Joint optimization---searching
for flips that improve both domains simultaneously---would likely
outperform naive stacking.

\subsection{Experiment~8: GSM8K Safety Check}

50~GSM8K word problems, generation with answer extraction:

\begin{table}[h]
\centering
\caption{GSM8K accuracy with and without patch (50~problems).}
\begin{tabular}{@{}lrr@{}}
\toprule
& Without patch & With patch \\
\midrule
Correct & 11/50 & 14/50 \\
Accuracy & 22.0\% & 28.0\% \\
\bottomrule
\end{tabular}
\end{table}

No degradation detected. The patch slightly improved accuracy (+3~problems),
likely within noise for $n=50$ but directionally positive. Our GSM8K accuracy (22\%) is below Bonsai's reported benchmark (88\%)
due to evaluation harness differences; the relative comparison is the
meaningful signal.

% ============================================================
\section{Limitations}
\label{sec:limitations}

\textbf{Evaluation harness limitations.} Our GSM8K accuracy (22\%) is
well below reported benchmarks, indicating evaluation setup differences.
Logit gap probes don't always predict generation outcomes (visible in
the $7\times8$ example). Standard benchmark evaluation with established
harnesses is a next step.

\textbf{Greedy search finds local optima.} Population-based evolutionary
search with crossover (XOR of XOR patches is a valid patch) could find
better solutions.

\textbf{Row-level granularity is coarse.} Each flip modifies 4,096~bits.
Per-group (128~bits) or per-bit search could produce more precise patches.

\textbf{Patch stacking shows interference.} Experiment~7 confirms
stacking is mechanically sound but behaviorally lossy---individual
improvements partially cancel. Joint optimization would likely
outperform naive stacking.

\textbf{Single model.} Bonsai~8B is currently the only production-quality
true 1-bit LLM. The approach does not extend to ternary models.

\textbf{Scale factors are not patched.} Only binary weights are modified,
not FP16 scale/bias values.

\textbf{Small evaluation set.} Our probes cover limited domains.

% ============================================================
\section{Responsible Use}

Bankai modifies model behavior with kilobyte-scale patches invisible at
inference time. The same mechanism could insert subtle malicious changes.
However, XOR patches are transparent by design: every patch is a readable
manifest listing exactly which rows were flipped, and verification is
trivial. If patch libraries become a deployment pattern, provenance and
verification become critical infrastructure.

% ============================================================
\section{Future Work}

\begin{itemize}[nosep]
  \item \textbf{Finer granularity:} Group-level (128~bits) or per-bit
    search for more precise patches.
  \item \textbf{Evolutionary search:} Population-based with crossover
    via XOR and Hamming-distance diversity pressure.
  \item \textbf{Benchmark evaluation:} MMLU subcategories, GSM8K,
    HumanEval.
  \item \textbf{Patch stacking:} Empirical composability testing.
  \item \textbf{Cross-model extraction:} XOR between Bonsai variants
    as naturally occurring patches.
  \item \textbf{Calculus-specific layer selection:} Searching layers~5,
    6, and~10 (identified as high-impact for calculus).
\end{itemize}

% ============================================================
\section{Conclusion}

We have introduced Bankai, the first post-training adaptation method for
true 1-bit LLMs. By exploiting the binary nature of weights, behavioral
modifications reduce to sparse XOR bitmasks that are orders of magnitude
smaller than existing adapters, incur zero inference overhead, and can be
applied and reverted in microseconds.

Through eight experiments on Bonsai~8B, we characterized the method's
capabilities and limitations: targeted corrections work reliably,
generalization requires diverse training signal, and the overall approach
represents a new point in the adaptation design space---one that is
uniquely enabled by true binary model architectures.

Code, patches, and all experiments are available at
\url{https://github.com/nikshepsvn/bankai}.

% ============================================================
\bibliographystyle{plainnat}
\begin{thebibliography}{12}

\bibitem[Hu et~al.(2021)]{hu2021lora}
E.~J. Hu, Y.~Shen, P.~Wallis, Z.~Allen-Zhu, Y.~Li, S.~Wang, L.~Wang,
  and W.~Chen.
\newblock Lo{RA}: Low-rank adaptation of large language models.
\newblock \emph{arXiv:2106.09685}, 2021.

\bibitem[Rakin et~al.(2019)]{rakin2019bitflip}
A.~S. Rakin, Z.~He, and D.~Fan.
\newblock Bit-flip attack: Crushing neural network with progressive bit
  search.
\newblock In \emph{ICCV}, 2019.

\bibitem[Dong et~al.(2024)]{dong2024stbllm}
P.~Dong, et~al.
\newblock {STBLLM}: Breaking the 1-bit barrier with structured binary
  {LLMs}.
\newblock In \emph{ICLR}, 2025.

\bibitem[Wang et~al.(2023)]{wang2023bitnet}
H.~Wang, S.~Ma, L.~Dong, S.~Huang, H.~Wang, L.~Ma, F.~Yang, R.~Wang,
  Y.~Wu, and F.~Wei.
\newblock Bit{N}et: Scaling 1-bit transformers for large language models.
\newblock \emph{arXiv:2310.11453}, 2023.

\bibitem[Ma et~al.(2025)]{ma2025bitnet}
S.~Ma, H.~Wang, S.~Huang, et~al.
\newblock Bit{N}et b1.58 2{B}4{T} technical report.
\newblock \emph{arXiv:2504.12285}, 2025.

\bibitem[{PrismML}(2026)]{prismml2026}
{PrismML}.
\newblock Bonsai 8{B}.
\newblock \url{https://prismml.com/news/bonsai-8b}, 2026.

\bibitem[Meng et~al.(2022)]{meng2022rome}
K.~Meng, D.~Bau, A.~Andonian, and Y.~Belinkov.
\newblock Locating and editing factual associations in {GPT}.
\newblock In \emph{NeurIPS}, 2022.

\bibitem[Meng et~al.(2023)]{meng2023memit}
K.~Meng, A.~S. Sharma, A.~Andonian, Y.~Belinkov, and D.~Bau.
\newblock Mass-editing memory in a transformer.
\newblock In \emph{ICLR}, 2023.

\bibitem[Bai et~al.(2021)]{bai2021tbfa}
Y.~Bai, et~al.
\newblock Targeted attack against deep neural networks via flipping limited
  weight bits.
\newblock In \emph{ICLR}, 2021.

\bibitem[Xu et~al.(2024)]{xu2024recast}
Y.~Xu, et~al.
\newblock {RECAST}: Reparameterized, compact weight adaptation for
  sequential tasks.
\newblock \emph{arXiv:2411.16870}, 2024.

\bibitem[Bulat and Tzimiropoulos(2020)]{bulat2020xornet}
A.~Bulat and G.~Tzimiropoulos.
\newblock {XOR-Net}: An efficient computation pipeline for binary neural
  network inference on edge devices.
\newblock 2020.

\bibitem[Rastegari et~al.(2016)]{rastegari2016xnor}
M.~Rastegari, V.~Ordonez, J.~Redmon, and A.~Farhadi.
\newblock {XNOR-Net}: Image{N}et classification using binary convolutional
  neural networks.
\newblock In \emph{ECCV}, 2016.

\bibitem[Dettmers et~al.(2023)]{dettmers2023qlora}
T.~Dettmers, A.~Pagnoni, A.~Holtzman, and L.~Zettlemoyer.
\newblock {QLoRA}: Efficient finetuning of quantized language models.
\newblock In \emph{NeurIPS}, 2023.

\end{thebibliography}

\end{document}
